 

### 2023-05-16 paper3.Rmd
Revisions to tables, revised submission to ProQuest

\begin{spacing}{1}

$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d mhealth_{di} + 
\ \ \ \ \ $$
$$\beta_d time_t*mhealth_{di} + \delta_{d} Post_i*mhealth_{di} + \gamma_d time_t*Post_i*mhealth_{di} + \theta_g + T^{'}_t\chi + \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
\end{spacing}

@@

Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals ( \acr{CIs}) using heteroskedasticity-robust standard errors.

>>>>

\begin{spacing}{1}
$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d mhealth_{di} + 
\ \ \ \ \ $$
$$\beta_d time_t*mhealth_{di} + \delta_{d} Post_i*mhealth_{di} + \gamma_d time_t*Post_i*mhealth_{di} + \theta_g + T^{'}_t\chi + \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
\end{spacing}

@@

Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (\acr{CIs}) using heteroskedasticity-robust standard errors.
